Network Data Collection for Artificial Intelligence

### 2020-04-03 research/paper2/paper2.tex
First gns3 server setup

\title{Network Data Collection for Artifical Intelligence
}

@@

\begin{IEEEkeywords}
artifical intelligence, neural networks, computer networks, network security, data collection
\end{IEEEkeywords}

@@

This paper is split in three chapters. The first chapter compares available network simulators and their software interfaces and explores possibilities for their automated setup based on the scenario and parameters. The second chapter focuses on tools to record the network traffic. In the third chapter methods of feature extraction and label definition are covered. This information serves as foundation for the further implementation of a system for automated data collection for artifical intelligence.

>>>>

\title{Network Data Collection for Artificial Intelligence}

@@

\begin{IEEEkeywords}
artificial intelligence, neural networks, computer networks, network security, data collection
\end{IEEEkeywords}

@@

This paper is split in three chapters. The first chapter compares available network simulators and their software interfaces and explores possibilities for their automated setup based on the scenario and parameters. The second chapter focuses on tools to record the network traffic. In the third chapter methods of feature extraction and label definition are covered. This information serves as foundation for the further implementation of a system for automated data collection for artificial intelligence.
